---
title: "Fable - hierarchical forecasting with synthetic data"
author: "Ciaran Gilbert"
date: "`r format(Sys.Date(),'%d-%m-%Y')`"
output:
  html_document:
    code_folding: show
    theme: united
    number_sections: yes
    toc: yes
  pdf_document:
    toc: yes
---

<style>
.main-container {
    max-width: 1200px !important;
}
pre {
  overflow-x: auto;
}
pre code {
  word-wrap: normal;
  white-space: pre;
}
</style>

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 800)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First some required packages


```{r message=FALSE, warning=FALSE, results='hide'}

packages <- c("fpp3", "data.table")


install.packages(setdiff(packages, rownames(installed.packages())))

rm(list=ls())

library(fpp3)
library(data.table)

```
First let's load the data

```{r}

cutoff <- yearmonth('1960-04-01')
y <- fread("./data/synthetic.csv")
y[,timepoints:=yearmonth(timepoints)]
y


```


Convert to a tsibble

```{r}

y_bl <- as_tsibble(y, key = c("l3_agg", "l2_agg", "l1_agg"), index = timepoints)
y_bl

```

Test out aggregation function

```{r}

y_bl %>%
  # Specify hierarchy
  aggregate_key(l3_agg / l2_agg / l1_agg, value = sum(passengers))


```


Make the hierarchical forecasts

* note top down proportions was giving me an error
* the mint_cov method is also not pos def

```{r}



fcsts <- y_bl %>%
  filter(timepoints <= cutoff) %>%
  # Specify hierarchy
  aggregate_key(l3_agg / l2_agg / l1_agg, value = sum(passengers)) %>%
  # Fit models
  model(base_fc = AR(value ~ 1 + order(p=1))) %>%
  # Set up reconciliation
  mutate(bu = bottom_up(base_fc),
         ols = min_trace(base_fc, method="ols"),
         wls_str = min_trace(base_fc, method = "wls_struct"),
         # td_fcst = top_down(base_fc, method = "forecast_proportions"),
         # mint_cov = min_trace(base_fc, method = "mint_cov"),
         mint_shrink = min_trace(base_fc, method = "mint_shrink"),
         wls_var = min_trace(base_fc, method = "wls_struct")) %>%
  # Produce the forecasts
  forecast(h = 8)

fcsts

```

Now combine with test data 

```{r}

y_test <-y_bl %>%
  filter(timepoints > cutoff) %>%
  aggregate_key(l3_agg / l2_agg / l1_agg, value = sum(passengers))

fcsts <- fcsts %>%
  as_tibble() %>%
  select(-value) %>%
  left_join(y_test, by=c("l3_agg", "l2_agg", "l1_agg", "timepoints"))


fcsts
```

Calculate the RMSE

```{r}

errors <- fcsts %>%
  mutate(error = (value - .mean)^2) %>%
  group_by_at(c('.model')) %>%
  summarise(rmse = sqrt(mean(error)))


names(errors$rmse) <- errors$.model
round(errors$rmse, 3)

```



```{r}

sessionInfo()


```






